Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-04-03 doc/PRF2022/Reviews/ResponseToReviewer1.tex

\begin{itemize}
  \item {\bf Response to Summary}: We thank the Reviewer for their
    positive assessment of our manuscript.  
%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

\noindent
\comment{My main criticism is the following: 1. Unilamellar,
multilamellar and striated structured are subjected to various flow
conditions, with increasing shear rate or strength of the flow (for TG
case). For all structures in both flows, the main result is that these
structures break eventually either for increased shear rate or increased
flow rate. But this is expected. What do all these results mean? I feel
that a constructive message is missing.}

\begin{itemize}
  \item[] {\bf Response:}
    The Results Section V of our first submission analyzed simulation
    data on a case-by-case basis. This made it unnecessarily difficult
    for the reader to make meaningful connections and we agree with the
    Reviewer: a constructive message was missing. Moreover, the
    large-shear-rate simulation runs for the most part corresponded to
    breakage in JP phases.

    To address these deficiencies, we performed additional simulations
    for moderate shear rates ranging from $0$ ns$^{-1}$ to $0.1$
    ns$^{-1}$ in shear flow and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$
    in TG flow. These additional data allowed us to examine material
    properties in greater detail: the new
    \begin{itemize}
      \item[$\bullet$] Figure 3 summarizes the strain and alignment data
        under \emph{all} flow and JP-type conditions.
      \item[$\bullet$] Figure 4 characterizes the change in free and binding energies.
      \item[$\bullet$] Figure 5 plots pre-rupture
        shear stress against shear rate revealing the rheological properties of
        the three distinct JP phases.    
    \end{itemize}
    A constructive message---identification a critical shear rate,
    relative binding strengths as a function of JP type,
    and effective viscosities and presence of shear thinning---is
    now formulated thanks to exploring the full range of
    shear rates.

@@

    Finally, we normalized the TG flow rate (previously $V_0$)
    so that we can compare the shear and TG flow in terms of the same
    shear rate $\dot \gamma$.  See page 11, equation (24) and page 12,
    top paragraph.
\end{itemize}

\noindent
\comment{2. And the discussion section is not written well. Please write it
properly.}
    \begin{itemize}
    \item[] {\bf Response:}
      To address this,
      we rewrote the Results section from scratch
    to what is now Section V ``Results and Discussion''.
    We highlighted the section heading on page 11 to indicate
    that the entire section is rewritten.
